Deep Multimodal Generative Models for Weakly-Supervised Learning

### 2017-11-18 paper/draft.tex
Finished project update

\begin{figure}[!h]
\centering
    \begin{subfigure}[b]{.24\linewidth}
        \centering
        \includegraphics[width=\linewidth]{multimnist_mmvae_image_sample.png}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{.24\linewidth}
        \centering
        \includegraphics[width=\linewidth]{multimnist_mmvae_condition_image_text_1773_image_sample.png}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{.24\linewidth}
        \centering
        \includegraphics[width=\linewidth]{multimnist_mmvae_condition_text_1773_image_sample.png}
        \caption{}
    \end{subfigure}
    \caption{\emph{MultiMNIST Dataset}: (a) Image samples from $z \sim N(0, 1)$. (b) Image samples from $p(z|x=1773,y=1773)$. (c) Image samples from $p(z|y=1773)$. The quality of the samples from (b) and (c) are almost identical.}
    \label{fig:multimnist:samples}
\end{figure}

>>>>

\begin{figure}[!h]
\centering
    \begin{subfigure}[b]{.24\linewidth}
        \centering
        \includegraphics[width=\linewidth]{multimnist_mmvae_image_sample.png}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{.24\linewidth}
        \centering
        \includegraphics[width=\linewidth]{multimnist_mmvae_condition_image_text_1773_image_sample.png}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{.24\linewidth}
        \centering
        \includegraphics[width=\linewidth]{multimnist_mmvae_condition_text_1773_image_sample.png}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{.24\linewidth}
        \centering
        \includegraphics[width=\linewidth]{multimnist_mmvae_condition_on_image_1773_image_sample.png}
        \caption{}
    \end{subfigure}

    \begin{subfigure}[b]{.24\linewidth}
        \centering
        \includegraphics[width=\linewidth]{multimnist_mmvae_condition_on_image_text_417_image_sample.png}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{.24\linewidth}
        \centering
        \includegraphics[width=\linewidth]{multimnist_mmvae_condition_on_text_417_image_sample.png}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{.24\linewidth}
        \centering
        \includegraphics[width=\linewidth]{multimnist_mmvae_condition_on_image_417_image_sample.png}
        \caption{}
    \end{subfigure}

    \begin{subfigure}[b]{.24\linewidth}
        \centering
        \includegraphics[width=\linewidth]{multimnist_mmvae_condition_on_image_12_image_sample.png}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{.24\linewidth}
        \centering
        \includegraphics[width=\linewidth]{multimnist_mmvae_condition_on_text_12_image_sample.png}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{.24\linewidth}
        \centering
        \includegraphics[width=\linewidth]{multimnist_mmvae_condition_on_image_12_image_sample.png}
        \caption{}
    \end{subfigure}

    \caption{\emph{MultiMNIST Dataset}: (a) Image samples from $z \sim N(0, 1)$. (b) Image samples from $p(z|x=1773,y=1773)$. (c) Image samples from $p(z|y=1773)$. (d) Image samples from $p(z|x=1773)$. (e) Image samples from $p(z|x=417,y=417)$. (f) Image samples from $p(z|y=417)$. (g) Image samples from $p(z|x=417)$. (h) Image samples from $p(z|x=12,y=12)$. (i) Image samples from $p(z|y=12)$. (j) Image samples from $p(z|x=12)$. The quality of samples is consistent across number of digits in the canvas. Using image-only, text-only, or both modalities also produce similarly crisp samples.}
    \label{fig:multimnist:samples}
\end{figure}

\begin{table}[!h]
    \centering
    \begin{tabular}{ l | c | c | c | c | c }
        (a) & 93 & 288 & 403 & 9926 & 21 \\
        \hline
        (b) & 1773 & 1773 & 1773 & 1773 & 1773 \\
        \hline
        (c) & 1773 & 1773 & 1773 & 1773 & 1773 \\
        \hline
        (d) & 1773 & 1773 & 1773 & 1673 & 1773 \\
        \hline
        (e) & 417 & 417 & 417 & 417 & 417 \\
        \hline
        (f) & 417 & 417 & 417 & 417 & 417 \\
        \hline
        (g) & 417 & 417 & 417 & 417 & 417 \\
        \hline
        (h) & 21 & 21 & 21 & 21 & 21 \\
        \hline
        (i) & 21 & 21 & 21 & 21 & 21 \\
        \hline
        (j) & 21 & 21 & 21 & 21 & 21 \\
        \newline
    \end{tabular}
    \caption{\emph{MultiMNIST Dataset}: Generated text samples from MMVAE trained on MultiMNIST. (a) Text samples from $z \sim N(0, 1)$. (b) Text samples from $p(z|x=1773,y=1773)$. (c) Text samples from $p(z|x=1773)$. (d) Text samples from $p(z|y=1773)$. (e) Text samples from $p(z|x=417,y=417)$. (f) Text samples from $p(z|y=417)$. (g) Text samples from $p(z|x=417)$. (h) Text samples from $p(z|x=12,y=12)$. (i) Text samples from $p(z|y=12)$. (j) Text samples from $p(z|x=12)$.}
    \label{table:mnist:samples}
\end{table}
